Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-03-29 WRITEUP/ms.tex
about to run out of battery. first comments on 6.  (I meant 5-6 in last commit msg).

The MCCs of \flower has dynamics largely similar to those observed in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies, in terms of their velocity dispersions, sizes, and gas surface densities (\Fig{larsons_single}; see e.g., \citealt{Swinbank11a}), with sizes of the order of $R\simeq$\,100\,pc and velocity dispersions of $\sigma\simeq$\,20$-$80\,\kms.
%
% velocity dispersion, larsons
%
Their velocity dispersions are also comparable to those observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a}), which lies along the locus of $\sigma\propto R^{0.56}$. Such high velocity dispersions and surface densities are expected since they are located in the nuclear regions of the galaxy, where the potential well is also deep. The higher velocity dispersions
(see footnote~\ref{ftn:veldisp} on page \pageref{ftn:veldisp}) of these MCCs can also be understood as they have experienced more recent episodes of \SF as \flower is assembling its stellar mass (these MCCs also have higher stellar-to-gas mass ratios of $\sim$60).
%
In fact, by the accretion stage (see \Fig{SFH}a) at $z\simeq$\,7.2, 
\flower has assembled a stellar mass of $M_\star$\eq7.5\E{9}\,\Msun. Thus, the higher velocity dispersion is due in part to the stronger stellar feedback compared to e.g., MCCs in its satellites ($\sigma\simeq$10\,\kms).

>>>>

The MCCs of \flower have dynamics largely similar to those observed in
$z$\ssim2 spatially resolved studies of gas-rich star-forming
galaxies, in terms of their velocity dispersions, sizes, and gas
surface densities (\Fig{larsons_single}; see e.g.,
\citealt{Swinbank11a}), with sizes of the order of $R\simeq$\,100\,pc
and velocity dispersions of $\sigma\simeq$\,20$-$80\,\kms. 
\MM{They agree in $\sigma$ vs.\ $R$, but their virial parameters seem
  high compared to the data sets provided, particularly for their
  relatively low surface densities (Figs.\ 5, 6).}
%
% velocity dispersion, larsons
%
Their velocity dispersions are also comparable to those observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a}), which lies along the locus of $\sigma\propto R^{0.56}$. Such high velocity dispersions and surface densities are expected since they are located in the nuclear regions of the galaxy, where the potential well is also deep. The higher velocity dispersions
(see footnote~\ref{ftn:veldisp} on page \pageref{ftn:veldisp}) of
these MCCs can also be understood as they have experienced more recent
episodes of \SF as \flower is assembling its stellar mass (these MCCs
also have higher stellar-to-gas mass ratios of $\sim$60). \MM{This is
  an enormous stellar to gas mass ratio, suggesting the clouds are
  completely controlled by the gravitational potential of the stars.
  A normal molecular cloud would have a ratio of < 0.1!  The
  implications of this for the apparent virial parameters and velocity
dispersions need to be considered much more carefully than they have been.}
%
In fact, by the accretion stage (see \Fig{SFH}a) at $z\simeq$\,7.2, 
\flower has assembled a stellar mass of $M_\star$\eq7.5\E{9}\,\Msun. Thus, the higher velocity dispersion is due in part to the stronger stellar feedback compared to e.g., MCCs in its satellites ($\sigma\simeq$10\,\kms).
